Efficient pedigree recording for fast population genetics simulation

### 2018-01-14 forwards_paper.tex

Another application of our methods would be the case of simulating coalescent histories conditional on known pedigrees.
The standard description of the Wright-Fisher coalescent averages over pedigrees.  However, conditional on a realized
pedigree, the distribution of coalescent times in the recent past differs from that of the unconditional coalescent
\citep{Wakeley2012-kw}.  For populations with known pedigrees \citep[\textit{e.g.}][]{Aguillon2017-ac}, it may be of use to
simulate transmission along such pedigrees for the purpose of inference.

@@

%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
Thanks to Jared Galloway, Brad Shaffer, and Evan McCartney--Melstad for useful discussions.
Work on this project was supported by funding from
the Sloan Foundation and the NSF (under DBI-1262645) to PR;
the Wellcome Trust (grant 100956/Z/13/Z to Gil McVean);
and XXX.

>>>>

@@

%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
Thanks to Jared Galloway, Brad Shaffer, and Evan McCartney--Melstad for useful discussions.
Work on this project was supported by funding from
the Sloan Foundation and the NSF (under DBI-1262645) to PR;
the Wellcome Trust (grant 100956/Z/13/Z to Gil McVean);
and NIH grant R01GM115564 to KRT.
